Aldebaran~b's temperate past uncovered in planet search data

### 2018-02-23 paper/aldebaran.tex
Close #3
Re-configured Figure 1 to fit better into the available space (the units
were cut off).
Close #6.
Show plot of model against data in appendix.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{all-data.pdf}
\caption{All archival and new radial velocities used for inference in this work.}
\label{alldata}
\end{figure}

@@

Our preferred model for the data uses one decaying mode and one oscillatory mode
in the CARMA process to capture the un-resolved superposition of many
asteroseismic modes (see Section \ref{sec:planet-star-parameters}); we have fit
models with more than one mode of each type, but find no improvement in
model-selection criteria from the expanded parameter space.  The priors we
impose in all cases on the parameters of the CARMA model, planetary RV signal,
and instrumental and site effects are given in Table \ref{tab:parameters}.

>>>>

\begin{figure}
\centering
\plotone{all-data.pdf}
\caption{All archival and new radial velocities used for inference in this work.  The site and instrument for each data set is indicated in the legend (see text for a full description).}
\label{alldata}
\end{figure}

@@

Our preferred model for the data uses one decaying mode and one oscillatory mode
in the CARMA process to capture the un-resolved superposition of many
asteroseismic modes (see Section \ref{sec:planet-star-parameters}); we have fit
models with more than one mode of each type, but find no improvement in
model-selection criteria from the expanded parameter space.  The priors we
impose in all cases on the parameters of the CARMA model, planetary RV signal,
and instrumental and site effects are given in Table \ref{tab:parameters}.  A
draw from the posterior for our canonical model in shown in data space in Figure
\ref{fig:data-space}.

\begin{figure}
\plotone{data-space}

\caption{\label{fig:data-space} A posterior draw from our model plotted with the
observed radial velocities.  Each site's radial velocity has been shifted by the
model's site-specific RV offset and errorbars have been scaled by the model's
site-specific errorbar scaling.  Data colors are as in Figure \ref{alldata}.
The black line gives the sum of the model's Keplerian component and the mean of
the inferred stochastic component; the dark and light bands give the 1- and
2-sigma uncertainty in the inferred stochastic component.  Between observations,
the uncertainty in the stochastic component increases; it reduces near
observations, as each observation provides some information about the stellar
noise that propogates to nearby times because of the temporal correlation in the
noise.  Stellar oscillations are apparent in the short-timescale wiggles in the
stochastic component between nearby observations; there is also a significant
long-period correlated component (represented in our model by an
exponentially-decaying eigenmode).}

\end{figure}
